Scalar Feedback based Joint Time-Frequency Precoder Interpolation for MIMO-OFDM Systems

### 2020-04-30 paper/response_letter_2.tex

\textbf{Reviewer 2}\\

\textbf{It is still not clear how the transmitter can obtain the
  future precoder parameters.
  Could you use an example to explain it?}

We appreciate the reviewer's concern. We feel that the word ``future''
is incorrect, and have clarified in the manuscript that past estimates
are improved as parameters come in. Here is an example.

Consider the 10th OFDM frame. All precoder parameters are calculated
using the parameters obtained at the 10th, 9th, 8th ... frames to fill
in the missing precoders. While at this process, the information
obtained during the 10th precoder can improve the precoder estimates
for the 9th, 8th etc. precoders. Naturally, these ``past'' precoder
parameters cannot be used directly for precoding, but the reduced
error that they have can improve the prediction and interpolation for
the precoders in the 11th frame. It is in this spirit that we ``walk
back'' to improve past estimates so that their contribution to future
predictions would possess less error. We have now clarified this in
the manuscript as well, as follows:

\emph{Precoder estimates are calculated using
the current and past data, though the earlier precoder estimates
arexsa improved by refining the past past estimates through
interpolation with current estimates (indicated by the black arrow in
Fig. 1).}

In addition, we have now indicated the reverse arrow in Fig. 1 with a
different colour and have clarified the refinement aspect in the
caption. We believe that this should clarify this aspect suitably.
\end{document}

### 2020-05-03 paper/main.tex
updating figure and description

\includegraphics[width=0.7\columnwidth]{images/new-adpm.pdf}

@@

  quantized. We see that the subcarrier indicated by
  red arrows has a precoder whose parameters are determined jointly
  using the neighbouring parameters, both in time and frequency.}

@@

% \vspace{-1\baselineskip}
\subsection{Joint Time Frequency Interpolation}
\label{interp}
After obtaining the $\beta$ values (using the single bit feedback) at
the transmitter, we can construct the precoder at subcarrier indices
$pk$ or $pk+q$, keeping with the same notation as the previous
section. 
% To construct precoders for the rest of the subcarriers, we will use
% precoder parameters from both the ``past'' and ``future'' time
% instances to do the interpolation (using backtracking to ensure
% causality). When using future time instances, the implication is that the precoder
% estimation is improved at a later time instant i.e. after receiving
% the feedback of the next set of subcarriers. Note that the precoder
% used for transmission is causally obtained, while the ``future''
% correction of past precoders merely improves the interpolation
% accuracy. 
In Fig.~\ref{fig:adpm-fig}, each parameter is interpolated using the
neighbouring subcarriers using bilinear interpolation (equivalent to
linear interpolation in two dimensions). These interpolated values are
then used to reconstruct the precoding matrices all together by
applying the reverse transformation of breaking the precoder into
independent parameters as given in Equation~\ref{eq:decompose}. To
improve the precoder estimates and interpolation accuracy, we ``walk
back'' to improve the past estimates by interpolating using current
estimates (although the current estimates only use data
causally). Thus, the approach here is able to exploit the time and
frequency correlation jointly to enhance performance.
% To construct the precoders for the rest of the subcarriers, we will
% use the  parameters from the previously determined subcarriers.
%

>>>>

\includegraphics[width=0.68\columnwidth]{images/new-adpm2.pdf}

@@

  quantized. Subcarriers indicated by red shaded cells have precoders 
  whose parameters are determined using the neighbouring parameters
  (shown via red arrows), both in time and frequency. The black arrow 
  indicates refinement of past precoders as fresher estimates are made
  available.}

@@

% \vspace{-1\baselineskip}
\subsection{Joint Time Frequency Interpolation}
\label{interp}
After obtaining the $\beta$ values (using the single bit feedback) at
the transmitter, we can construct the precoder at subcarrier indices
$pk$ or $pk+q$, keeping with the same notation as the previous
section. 
% To construct precoders for the rest of the subcarriers, we will use
% precoder parameters from both the ``past'' and ``future'' time
% instances to do the interpolation (using backtracking to ensure
% causality). When using future time instances, the implication is that the precoder
% estimation is improved at a later time instant i.e. after receiving
% the feedback of the next set of subcarriers. Note that the precoder
% used for transmission is causally obtained, while the ``future''
% correction of past precoders merely improves the interpolation
% accuracy.

In Fig.~\ref{fig:adpm-fig}, each parameter is interpolated using the
neighbouring subcarriers using bilinear interpolation (equivalent to
linear interpolation in two dimensions). These interpolated values are
then used to reconstruct the precoding matrices all together by
applying the reverse transformation of breaking the precoder into
independent parameters as given in
Equation~\ref{eq:decompose}. Precoder estimates are calculated using
the current and past data, though the earlier precoder estimates
are improved by refining the past past estimates through
interpolation with current estimates (indicated by the black arrow in
Fig.~\ref{fig:adpm-fig}). Thus, the approach here is able to exploit
the time and frequency correlation jointly to enhance performance.

% To construct the precoders for the rest of the subcarriers, we will
% use the  parameters from the previously determined subcarriers.
%
